A finite-state morphological transducer for Kyrgyz

### 2012-03-13 paper/paper.tex
numbers for kywp

%FIXME: this should be closer to the 200 word limit, and less like the intro pargraph
\abstract{This paper describes the development of a morphological transducer oriented for the task of machine translation for the Kyrgyz language using the free/open-source platform HFST. The transducer was developed under the auspices of the Apertium \citep{forcada2011} project for use in a machine translation system from Turkish to Kyrgyz.}

@@

\begin{document}
\maketitleabstract{}
\thispagestyle{empty}

@@

\begin{table*}[htbp]
	\centering
	\begin{tabular}{lrrrr}
		\toprule
		Corpus           & Tokens    & Known     & Naïve coverage    & Mean ambiguity\\
		\midrule
		Kyrgyz Wikipedia & 329,524   & 269,573   & 81.84 $\pm$ 3.23  & 4.54\\
		RFERL Kyrgyzstan & 4,107,555 & 3,586,000 & 87.37 $\pm$ 1.23  & 4.46\\
		\bottomrule
	\end{tabular}
	\caption{FIXME}
	\label{table:cov}
\end{table*}

>>>>

%FIXME: this should be closer to the 200 word limit, and less like the intro pargraph
\abstract{This paper describes the development of a morphological transducer oriented for the task of machine translation for the Kyrgyz language using the free/open-source platform HFST. The transducer was developed under the auspices of the Apertium \citep{forcada2011} project for use in a machine translation system from Turkish to Kyrgyz.\\
\Keywords{kyrgyz, morphology, open-source}}

@@

\begin{document}
\maketitleabstract{}
\pagestyle{empty}

@@

\begin{table*}[htbp]
	\centering
	\begin{tabular}{lrrrr}
		\toprule
		Corpus           & Tokens    & Known     & Naïve coverage    & Mean ambiguity\\
		\midrule
		Kyrgyz Wikipedia & 329,524   & 270,668   & 82.11 $\pm$ 3.23  & 2.35\\
		RFERL Kyrgyzstan & 4,107,555 & 3,586,000 & 87.37 $\pm$ 1.23  & 4.46\\
		\bottomrule
	\end{tabular}
	\caption{FIXME}
	\label{table:cov}
\end{table*}
